Statistical analysis of periodic data in neuroscience

### 2021-01-07 manuscript/manuscript.Rmd
Implemented independent T-squared test. Replaced the tsq1.test function with tsqh.test (which can do both one and two sample tests).

All scripts used to generate this manuscript are available at: [https://github.com/bakerdh/FourierStats](https://github.com/bakerdh/FourierStats). This includes an _R_ package called _FourierStats_, featuring functions to implement a one-sample Hotelling's [-@Hotelling1931] $T^2$ statistic, Victor & Mast's [-@Victor1991] $T^2_{circ}$ statistic, and the condition index and $ANOVA^2_{circ}$ statistics proposed in this paper.

@@

tsqmatrix <- matrix(0,nrow=length(samplesizes),ncol=length(dlist))
circmatrix <- matrix(0,nrow=length(samplesizes),ncol=length(dlist))
for (n in 1:nsims){
  for (s in 1:length(samplesizes)){
    for (s2 in 1:length(dlist)){
    data <- matrix(rnorm(2*samplesizes[s]),nrow=samplesizes[s],ncol=2)
    data[,1] <- data[,1] + dlist[s2]
    a <- tsq1.test(data)
    if (a[5]<0.05){tsqmatrix[s,s2] <- tsqmatrix[s,s2] + 1}
    a <- tsqc.test(data)
    if (a[5]<0.05){circmatrix[s,s2] <- circmatrix[s,s2] + 1}
  }}
}

@@

    xdata <- rnorm(nobs,mean=0,sd=1)
    ydata <- sign(corvals[cond])*sqrt(abs(corvals[cond]))*xdata + sqrt(1-abs(corvals[cond]))*rnorm(nobs,mean=0,sd=1)
    simdata[,1] <- xdata
    simdata[,2] <- ydata
    output <- tsqc.test(simdata,paired=FALSE)
    if (output$p.value < 0.05){csig[cond] <- csig[cond] + 1}
    output <- tsq1.test(simdata)
    if (output$p.value < 0.05){hsig[cond] <- hsig[cond] + 1}
  }}
propc <- csig/nsims
lines(corvals,propc,lty=1,lwd=4,col=nbdtpal[2])
proph <- hsig/nsims
lines(corvals,proph,lty=1,lwd=4,col=nbdtpal[1])

@@

    output <- tsqc.test(simdata,paired=FALSE)
    if (output$p.value < 0.05){csig[cond] <- csig[cond] + 1}
    output <- tsq1.test(simdata)
    if (output$p.value < 0.05){hsig[cond] <- hsig[cond] + 1}
  }}
propc <- csig/nsims
lines(corvals,propc,lty=1,lwd=4,col=nbdtpal[2])
proph <- hsig/nsims
lines(corvals,proph,lty=1,lwd=4,col=nbdtpal[1])

>>>>

All scripts used to generate this manuscript are available at: [https://github.com/bakerdh/FourierStats](https://github.com/bakerdh/FourierStats). This includes a _Matlab_ toolbox and an _R_ package called _FourierStats_, featuring functions to implement Hotelling's [-@Hotelling1931] $T^2$ statistic, Victor & Mast's [-@Victor1991] $T^2_{circ}$ statistic, and the condition index and $ANOVA^2_{circ}$ statistics proposed in this paper.

@@

tsqmatrix <- matrix(0,nrow=length(samplesizes),ncol=length(dlist))
circmatrix <- matrix(0,nrow=length(samplesizes),ncol=length(dlist))
for (n in 1:nsims){
  for (s in 1:length(samplesizes)){
    for (s2 in 1:length(dlist)){
    data <- matrix(rnorm(2*samplesizes[s]),nrow=samplesizes[s],ncol=2)
    data[,1] <- data[,1] + dlist[s2]
    a <- tsqh.test(data)
    if (a[5]<0.05){tsqmatrix[s,s2] <- tsqmatrix[s,s2] + 1}
    a <- tsqc.test(data)
    if (a[5]<0.05){circmatrix[s,s2] <- circmatrix[s,s2] + 1}
  }}
}

@@

    xdata <- rnorm(nobs,mean=0,sd=1)
    ydata <- sign(corvals[cond])*sqrt(abs(corvals[cond]))*xdata + sqrt(1-abs(corvals[cond]))*rnorm(nobs,mean=0,sd=1)
    simdata[,1] <- xdata
    simdata[,2] <- ydata
    output <- tsqc.test(simdata,paired=FALSE)
    if (output$p.value < 0.05){csig[cond] <- csig[cond] + 1}
    output <- tsqh.test(simdata)
    if (output$p.value < 0.05){hsig[cond] <- hsig[cond] + 1}
  }}
propc <- csig/nsims
lines(corvals,propc,lty=1,lwd=4,col=nbdtpal[2])
proph <- hsig/nsims
lines(corvals,proph,lty=1,lwd=4,col=nbdtpal[1])

@@

    output <- tsqc.test(simdata,paired=FALSE)
    if (output$p.value < 0.05){csig[cond] <- csig[cond] + 1}
    output <- tsqh.test(simdata)
    if (output$p.value < 0.05){hsig[cond] <- hsig[cond] + 1}
  }}
propc <- csig/nsims
lines(corvals,propc,lty=1,lwd=4,col=nbdtpal[2])
proph <- hsig/nsims
lines(corvals,proph,lty=1,lwd=4,col=nbdtpal[1])
